---
title: "p8105_hw1_kw3104"
author: Carrie Wu
output: html_document
date: "2024-09-21"
---

## Question 1

```{r}
library(palmerpenguins)

data("penguins", package = "palmerpenguins")

```

* This data set include: species, island, bill_length_mm, bill_depth_mm, flipper_length_mm, body_mass_g, sex, and year.
  *Noted: row 4 and 272 containing missing values
* There are 344 rows and 8 columns
* The mean flipper length in the dataset is `r mean(penguins$flipper_length_mm, na.rm = TRUE)` mm.

```{r scatterplot, warning = FALSE}
library(ggplot2)

ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) +
  geom_point() 

ggsave("scatterplot_penguins.png", width = 6, height = 4)

```

## Question 2
* a random sample of size 10 from a standard Normal distribution
* a logical vector indicating whether elements of the sample are greater than 0
* a character vector of length 10
* a factor vector of length 10, with 3 different factor “levels”

```{r}
library(tibble)

example_df = tibble(
  samp = rnorm(10),
  vec_log = samp > 0,
  vec_char = c("q","w", "e","r","t","y","u","i","o","p"),
  vec_fac = factor(c("good","good","bad","good","neutral","bad","good","neutral","good","bad"))
)

```

mean of data frame
##execuation halted. 
```{r}
##The mean is `r mean(samp)`.
```



